%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Teaching team %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Teaching Team}
  \begin{itemize}
  \item \href{mailto:barak.pearlmutter@mu.ie}{\textbf{Barak A. Pearlmutter} $\langle \texttt{barak.pearlmutter@mu.ie} \rangle$}

    \medskip

    Professor, Dept of Computer Science. Working on neural networks since the second time they were cool. AI Doomer. Also into theoretical neurobiology and science fiction and functional programming languages and robust first-class automatic differentiation as an enabling technology for building adaptive systems.

    \medskip

    Office: 132 Eolas.

    Office hours: drop by anytime (especially Wed/Fri afternoons), or by appointment.

    \bigskip

  \item Imen Mourali

    \medskip

    Demonstrator. Python and Deep Learning Expert. GPU Wrangler. Problem solver.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Examination Regulations %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Assessment}
  \begin{block}{Final exam}
    \begin{itemize}
    \item Two hours.
    \end{itemize}
  \end{block}
  \pause
  \begin{block}{HW0: Deep Learning Exercise}
    \begin{itemize}
    \item Each student will get a training set and an unlabeled test set
    \item Submit test set labels \& what-I-did documentation
    \item Bakeoff: who did best?
    \end{itemize}
  \end{block}
  \pause
  \begin{block}{RL Project}
    \begin{itemize}[<+->]
      \item Do some RL and write it up.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{MURL-2026}
  \begin{block}{Course Conference called MURL-2026}
    \begin{itemize}[<+->]
    \item Each student does RL-related project; development in git.
    \item Submit blinded manuscript describing project to MURL-2026 (HotCRP web site)
    \item Abstracts (one ¶) have early deadline.
    \item Code also submitted (supplementary material).
    \item Manuscripts: rigid format (\LaTeX\ style/template), sections, page limit, deadline.
    \item Submissions and review process will be double-blind. Each student is a reviewer. There will be reviews, responses, discussion, revisions, meta-reviews, decisions.
    \item BP is the program \& publication chair.
    \item All submissions accepted as posters. Optional: oral spotlights, best paper award, most fun project award.
    \item The poster session will be open to the public.
    \end{itemize}
  \end{block}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Course Outline %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Course outline}
  The course will cover the following content:
  \medskip\pause
  \begin{itemize}[<+->]
  \item Conceptual basics and historical overview
  \item Markov decision processes
  \item Dynamic programming
  \item Monte Carlo learning
  \item Temporal difference learning
  \item Multi-step bootstrapping
  \item Planning and model-based RL
  \item Function approximation and (deep) learning
  \item Policy gradient methods
  \item Contemporary (deep) RL algorithms
  \item Further practical RL challenges (meta learning, safety, ...)
  \end{itemize}
\end{frame}
